Investigating Neolithic pottery usage in the Yanyuan Basin in Southwest China using organic residue analysis

### 2023-01-20 analysis/paper/paper.Rmd
editing the background section

<!--Info about Guijiabao-->
Among those archaeological sites in Yanyuan, Guijiabao located in the southwestern part of the basin is a unique site with relatively complete and continuous occupation from the early Neolithic period to the historical period [@Guijiabao2017a; @Guijiabao2017b]. Investigation in 2015 and subsequent excavations from 2016 to 2019 reveal abundant archaeological materials and features, such as semi-subterranean houses, ground houses, post holes, ash pits, ditches, and burials, suggesting that Guidiabao is a settlement site with long-term occupation [@Hao2022]. The chronology of Guijiabao can be divided into three temporal phases based on 19 radiocarbon dates from plant remains and a human bone, including the Neolithic period (5000-3700 BP.), the Bronze Age (3200-2700 BP.), and the late North Song to early Ming Dynasties (1200-500 BP.) [@Hao2022]. For the Neolithic period, it can be further separated into two subphases, 5000-4500 cal. BP and 4500-3700 cal. BP, according to the artifact assemblages and ceramic forms and styles. The archaeobotanical remains found at Guidiabao reveal the evidence of crop cultivation dominated by foxtail and broomcorn millet can be traced back to 5000 B.P and mixed cultivation of millet and rice in a later period (3000–1700 B.C) [@Guijiabao2014; @Hao2022].

<!--Info about Gaoshan-->
Gaoshan site is located in the southwestern part of Chengdu Plain.

>>>>

<!--Info about Guijiabao-->
Among those archaeological sites in Yanyuan, Guijiabao located in the southwestern part of the basin is a unique site with relatively complete and continuous occupation from the early Neolithic period to the historical period [@Guijiabao2017a; @Guijiabao2017b]. Survey in 2015 and subsequent excavations from 2016 to 2019 reveal abundant archaeological materials and features, such as semi-subterranean houses, ground houses, post holes, ash pits, ditches, and burials, suggesting that Guidiabao is a settlement site with long-term occupation [@Hao2022]. The chronology of Guijiabao can be divided into three temporal phases based on 19 radiocarbon dates from plant remains and a human bone, including the Neolithic period (5000-3700 BP), the Bronze Age (3200-2700 BP.), and the late North Song to early Ming Dynasties (1200-500 BP) [@Hao2022]. For the Neolithic period, it can be further separated into two subphases, 5000-4500 cal. BP and 4500-3700 cal. BP, according to the content of artifact assemblages and ceramic forms and styles. The archaeobotanical remains found at Guidiabao reveal the evidence of crop cultivation dominated by foxtail and broomcorn millet that can be traced back to 5000 BC and mixed cultivation of millet and rice in a later period (3000–1700 BC) [@Guijiabao2014; @Hao2022].

<!--Info about Gaoshan-->
Gaoshan site is located in the southwestern part of the Chengdu Plain. Excavations at Gaoshan unearthed house foundations, burials, ashpits with abundant materials that could represent the earliest phases of the Baodun culture [citations].
